method

### 2021-12-03 06_Paper/ER-ED/method.Rmd
added ANOVA output
corrected data structures

  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["instr_1"]], datalist_ER[[i]][["slider_arousal.response"]], datalist_ER[[i]][["slider_effort.response"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)), ]

@@

```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}

@@

@@

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = data_ER,
                          within = "block",
                          fun_aggregate = mean)

>>>>

  tmp = data.frame(datalist_ER[[i]][["participant"]], 
                   datalist_ER[[i]][["instr_1"]], 
                   datalist_ER[[i]][["slider_arousal.response"]], 
                   datalist_ER[[i]][["slider_effort.response"]],
                   datalist_ER[[i]][["TriggerBlockView"]],
                   datalist_ER[[i]][["TriggerBlockReg"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)), ]

@@

```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
## Subjective arousal

@@

# Figure to visualize arousal ratings

#ggplot2::ggplot

## Subjective effort

@@

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = data_ER,
                          within = "block",
                          fun_aggregate = mean)
afex::nice(aov.effort, es = "pes")
